---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Chr.Rpts.Hsapiens.dbSNP149.GRCh38p7

<!-- badges: start -->
<!-- badges: end -->

The goal of Chr.Rpts.Hsapiens.dbSNP149.GRCh38p7 is to provide dbSNP Chromosome
Reports' data in data frame format. The information made available by this
package is the one found in
ftp://ftp.ncbi.nih.gov/snp/organisms/human_9606_b149_GRCh38p7/.

## Installation

Because I use [Git LFS](https://git-lfs.github.com/) to track some of the files in this R package, you will need to have [Git LFS](https://git-lfs.github.com/) installed before installing this package. You can check if you have Git LFS already installed by running:

```bash
git lfs version
```

It should return Git LFS's version if installed, or a Git error: `git: 'lfs' is not a git command. See 'git --help'.`

If you don't have it installed already, and if you are on Ubuntu, you can install it with:

```bash
sudo apt-get update -y
sudo apt-get install -y git-lfs
```

Then, because of issues [#192](https://github.com/r-lib/remotes/issues/292), [#91584](https://community.rstudio.com/t/cant-access-data-in-a-package-that-i-created/91584), [#889](https://github.com/r-lib/devtools/issues/889), you need to clone this repository first and then install from the local folder generated on your computer:

```bash
# This will clone the repository to your home folder.
cd ~
git clone https://github.com/maialab/Chr.Rpts.Hsapiens.dbSNP149.GRCh38p7
```

And finally install Chr.Rpts.Hsapiens.dbSNP149.GRCh38p7 from the local folder (assuming it's in your home folder):

``` r
# install.packages("remotes")
remotes::install_local("~/Chr.Rpts.Hsapiens.dbSNP149.GRCh38p7")
```

If the installation went successful, you may remove the local folder `~/Chr.Rpts.Hsapiens.dbSNP149.GRCh38p7` (or other path if you cloned to another folder):

```bash
rm -rf ~/Chr.Rpts.Hsapiens.dbSNP149.GRCh38p7
```

## Usage

The package contains only one function which is `read_chr_rpt`. Browse this function help page (`?read_chr_rpt`) to know how to use it:

```{r}
library(Chr.Rpts.Hsapiens.dbSNP149.GRCh38p7)

chrom_Y <- read_chr_rpt('Y')

chrom_Y[1:10, 1:4]
```
